---
title: "Math Affect"
output: word_document
date: "`r Sys.Date()`"
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load Data
```{r}
library(mice)
library(tidyverse)
library(gtsummary)
library(jtools)
library(flextable)
library(survey)
library(haven)
library(mitools)
library(interactions)
```

```{r}
df_long <- read_dta("data/hsls_subset_long.dta")

df <- df_long %>% as_factor()

df$race_ethnicity <- relevel(df$race_ethnicity, ref = "Asian")
```

# Descriptive Statistics
```{r}
df_subset <- df %>% dplyr::select(adv_math, math_level,
                                  teach_treat_std, first_lang,
                                  early_algebra, scale_math_id, scale_math_eff, 
                                  scale_math_uti, scale_math_int, female, 
                                  ses_quintile, race_ethnicity, public, math_score, 
                                  time, urban, scale_math_eff, scale_math_uti)
df_subset %>% tbl_summary
```

## Alpha
```{r}
df_wide <- read_dta("data/hsls_subset_wide.dta")
df_alpha1 <- df_wide %>% dplyr::select(math_treat1, math_easy1, math_interest1)
df_alpha2 <- df_wide %>% dplyr::select(math_treat2, math_easy2, math_interest2)
psych::alpha(df_alpha1)
psych::alpha(df_alpha2)
```


# Unweighted Models

## Efficacy
```{r}
eff_lm <- lm(
  data = df,
  scale_math_eff ~ 
    time*math_level + teach_treat_std*math_level +
    ses + first_lang + female + race_ethnicity +
    math_score + early_algebra +
    public + urban )

summ(eff_lm)
```

## Identity
```{r}
id_lm <- lm(
  data = df,
  scale_math_id ~ 
    time*math_level + teach_treat_std*math_level +
    ses + first_lang + female + race_ethnicity +
    math_score + early_algebra +
    public + urban )

summ(id_lm)
```

## Interest

```{r}
int_lm <- lm(
  data = df,
  scale_math_int ~ 
    time*math_level + teach_treat_std*math_level +
    ses + first_lang + female + race_ethnicity +
    math_score + early_algebra +
    public + urban )

summ(int_lm)
```

## Utility
```{r}
uti_lm <- lm(
  data = df,
  scale_math_uti ~ 
    time*math_level + teach_treat_std*math_level +
    ses + first_lang + female + race_ethnicity +
    math_score + early_algebra +
    public + urban )

summ(uti_lm)
```
## Combined Table
```{r}
eff_lm_tbl <- eff_lm %>% tbl_regression() %>% add_significance_stars(hide_p = TRUE, hide_ci = TRUE, hide_se = TRUE)
id_lm_tbl <-  id_lm %>% tbl_regression()  %>% add_significance_stars(hide_p = TRUE, hide_ci = TRUE, hide_se = TRUE)
int_lm_tbl <- int_lm %>% tbl_regression() %>% add_significance_stars(hide_p = TRUE, hide_ci = TRUE, hide_se = TRUE)
uti_lm_tbl <- uti_lm %>% tbl_regression() %>% add_significance_stars(hide_p = TRUE, hide_ci = TRUE, hide_se = TRUE)

tbl_merge(list(eff_lm_tbl, id_lm_tbl, int_lm_tbl, uti_lm_tbl),
          tab_spanner = c("Self-Efficacy", "Identity", "Interest", "Utility")) %>% 
  as_flex_table()
```

# Weighted Models
## Weight Data
```{r}
df_brr <- svrepdesign(
  weights = ~w2w1stu, 
  repweights = "w2w1stu[001-200]",
  type = "BRR", 
  data = df,
  combined.weights = TRUE
)
```

## Efficacy
```{r}
eff_lm_svy <- svyglm(
  design = df_brr,
  scale_math_eff ~ 
    time*math_level + teach_treat_std*math_level +
    ses + first_lang + female + race_ethnicity +
    math_score + early_algebra +
    public + urban)

summ(eff_lm_svy)
```

## Identity
```{r}
id_lm_svy <- svyglm(
  design = df_brr,
  scale_math_id ~ 
    time*math_level + teach_treat_std*math_level +
    ses + first_lang + female + race_ethnicity +
    math_score + early_algebra +
    public + urban )

summ(id_lm_svy)
```

## Interest

```{r}
int_lm_svy <- svyglm(
  design = df_brr,
  scale_math_int ~ 
    time*math_level + teach_treat_std*math_level +
    ses + first_lang + female + race_ethnicity +
    math_score + early_algebra +
    public + urban )

summ(int_lm_svy)
```

## Utility
```{r}
uti_lm_svy <- svyglm(
  design = df_brr,
  scale_math_uti ~ 
    time*math_level + teach_treat_std*math_level +
    ses + first_lang + female + race_ethnicity +
    math_score + early_algebra +
    public + urban )

summ(uti_lm_svy)
```
## Combined Table
```{r}
eff_lm_tbl_svy <- eff_lm_svy %>% tbl_regression() %>% add_significance_stars(hide_p = TRUE, hide_ci = TRUE, hide_se = TRUE)
 id_lm_tbl_svy <-  id_lm_svy %>% tbl_regression() %>% add_significance_stars(hide_p = TRUE, hide_ci = TRUE, hide_se = TRUE)
int_lm_tbl_svy <- int_lm_svy %>% tbl_regression() %>% add_significance_stars(hide_p = TRUE, hide_ci = TRUE, hide_se = TRUE)
uti_lm_tbl_svy <- uti_lm_svy %>% tbl_regression() %>% add_significance_stars(hide_p = TRUE, hide_ci = TRUE, hide_se = TRUE)

tbl_merge(list(eff_lm_tbl_svy, id_lm_tbl_svy, int_lm_tbl_svy, uti_lm_tbl_svy),
          tab_spanner = c("Self-Efficacy", "Identity", "Interest", "Utility")) %>% 
  as_flex_table()
```

# Imputed Models

## Efficacy

```{r}
eff_lm_imp <- with(df_imp, lm(
  scale_math_eff ~ 
    time*math_level + teach_treat_std*math_level +
    ses + first_lang + female + race_ethnicity +
    math_score + early_algebra +
    public + urban))

summ(eff_lm_imp)
```

## Identity

```{r}
id_lm_imp <- with(df_imp, lm(
  scale_math_id ~ 
    time*math_level + teach_treat_std*math_level +
    ses + first_lang + female + race_ethnicity +
    math_score + early_algebra +
    public + urban))

summ(id_lm_imp)
```

## Interest

```{r}
int_lm_imp <- with(df_imp, lm(
  scale_math_int ~ 
    time*math_level + teach_treat_std*math_level +
    ses + first_lang + female + race_ethnicity +
    math_score + early_algebra +
    public + urban))

summ(int_lm_imp)
```

## Utility
```{r}
uti_lm_imp <- with(df_imp, lm(
  scale_math_uti ~ 
    time*math_level + teach_treat_std*math_level +
    ses + first_lang + female + race_ethnicity +
    math_score + early_algebra +
    public + urban))

summ(uti_lm_imp)
```


## Combined Table
```{r}
eff_lm_tbl_imp <- eff_lm_imp %>% tbl_regression() %>% add_significance_stars(hide_p = TRUE, hide_ci = TRUE, hide_se = TRUE)
 id_lm_tbl_imp <-  id_lm_imp %>% tbl_regression() %>% add_significance_stars(hide_p = TRUE, hide_ci = TRUE, hide_se = TRUE)
int_lm_tbl_imp <- int_lm_imp %>% tbl_regression() %>% add_significance_stars(hide_p = TRUE, hide_ci = TRUE, hide_se = TRUE)
uti_lm_tbl_imp <- uti_lm_imp %>% tbl_regression() %>% add_significance_stars(hide_p = TRUE, hide_ci = TRUE, hide_se = TRUE)

tbl_merge(list(eff_lm_tbl_imp, id_lm_tbl_imp, int_lm_tbl_imp, uti_lm_tbl_imp),
          tab_spanner = c("Self-Efficacy", "Identity", "Interest", "Utility")) %>% 
  as_flex_table()
```

# Imputed Weighted Models

## Weigh Data & Write Function
```{r}
# Creates a list of completed dataset for survey weights
imp_list <- imputationList(
  lapply(1:df_imp$m, function(i) complete(df_imp, i))
)

# creates BRR survey design
df_brr_imp <- svrepdesign(
  weights = ~w2w1stu, 
  repweights = "w2w1stu[001-200]",
  type = "BRR", 
  data = imp_list,
  combined.weights = TRUE
) 

# function to exponentiate results and create dataframe with or, se, ll, ul, & p-value
make_mi_table <- function(model) {
  as.data.frame(summary(MIcombine(model))) %>%  # make dataframe of pooled model
  tibble::rownames_to_column("variable") %>% # make variable column
  mutate(
    or = exp(results), # exponentiate estimate for ORs
    ll = exp(`(lower`), # exponentiate ll
    ul = exp(`upper)`), # exponentiate ul
    z = results / se, 
    p.value = 2 * (1 - pnorm(abs(z)))) # calculate p-value with Wald Test
}
```

## Efficacy
```{r}
eff_lm_imp_svy <- with(df_brr_imp, svyglm(
  scale_math_eff ~ 
    time*math_level + teach_treat_std*math_level +
    ses + first_lang + female + race_ethnicity +
    math_score + early_algebra +
    public + urban))

summary(MIcombine(eff_lm_imp_svy))

```

## Identity
```{r}
id_lm_imp_svy <- with(df_brr_imp, svyglm(
  scale_math_id ~ 
    time*math_level + teach_treat_std*math_level +
    ses + first_lang + female + race_ethnicity +
    math_score + early_algebra +
    public + urban))

summary(MIcombine(id_lm_imp_svy))

```

## Interest

```{r}
int_lm_imp_svy <- with(df_brr_imp, svyglm(
  scale_math_int ~ 
    time*math_level + teach_treat_std*math_level +
    ses + first_lang + female + race_ethnicity +
    math_score + early_algebra +
    public + urban))

summary(MIcombine(int_lm_imp_svy))

```

## Utility
```{r}
uti_lm_imp_svy <- with(df_brr_imp, svyglm(
  scale_math_uti ~ 
    time*math_level + teach_treat_std*math_level +
    ses + first_lang + female + race_ethnicity +
    math_score + early_algebra +
    public + urban))

summary(MIcombine(uti_lm_imp_svy))


```


## Combined Table
```{r}
eff_lm_tbl_imp_svy <- make_mi_table(eff_lm_imp_svy) %>% mutate(outcome = "efficacy")
id_lm_tbl_imp_svy <-  make_mi_table(id_lm_imp_svy) %>% mutate(outcome = "identity")
int_lm_tbl_imp_svy <- make_mi_table(int_lm_imp_svy) %>% mutate(outcome = "interest")
uti_lm_tbl_imp_svy <- make_mi_table(uti_lm_imp_svy) %>% mutate(outcome = "utility")

imp_svy_tbl <- cbind(eff_lm_tbl_imp_svy, id_lm_tbl_imp_svy)
imp_svy_tbl <- cbind(imp_svy_tbl, int_lm_tbl_imp_svy)
imp_svy_tbl <- cbind(imp_svy_tbl, uti_lm_tbl_imp_svy)

imp_svy_tbl %>% as_flextable()

```
